---
title: "Part 1 to explore & find adstock, diminishing ret"
output: 
  html_notebook:
    highlight: tango
    df_print: paged
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
    number_sections: false
    toc_depth: 6
---



```{r}
library(tidyverse)
library(lubridate)
library(caret)
```

### Data

```{r}
readxl::read_xlsx("../Adstock - diminishing MMM.xlsx", sheet = "Raw Data") %>% 
  mutate(Date = as.integer(Date),
         Date = as.Date(Date, origin = "1900-01-01")) 
```


```{r}
df <- readxl::read_xlsx("../Adstock - diminishing MMM.xlsx", sheet = "Raw Data") %>% 
  mutate(s.no = row_number()) 

df
```

### smpl Regr.


```{r}
df %>% 
  caret::train(sales ~ FB + TV, data = ., method = "lm") %>% 
  summary()
```



```{r}
df %>% 
  caret::train(sales ~ FB, data = ., method = "lm") %>% 
  summary()
```

```{r}
df %>% 
  caret::train(sales ~ TV, data = ., method = "lm") %>% 
  summary()
```

```{r}
df %>% 
  caret::train(sales ~ Radio, data = ., method = "lm") %>% 
  summary()
```



```{r}
model_smpl <- df %>% 
  select(sales:Radio) %>% 
  caret::train(sales ~ ., data = ., method = "lm")

model_smpl
```

```{r}
summary(model_smpl)
```

```{r}
ggplot(varImp(model_smpl))
```

#### var imp

```{r}
predctn_model_smpl <- predict(model_smpl, df)

predctn_model_smpl
```

#### regr results df

```{r}
df_results <- cbind(df, predctn_model_smpl)

df_results
```

#### plot results Vs orig

```{r}
df_results %>% 
  ggplot(aes(x = Time, y = sales)) +
  geom_line(group = 1) +
  geom_line(aes(y = predctn_model_smpl), group = 1)
```


```{r}
df_results %>% 
  pivot_longer(cols = c(sales,predctn_model_smpl), names_to = "series", values_to = "output") %>% 
  mutate(series = as_factor(series)) %>% 
  
  ggplot(aes(x = Time, y = output, col = series, group = series)) +
  geom_line(size = 1) +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90))
```

#### Rsq, RMSE,MAE

```{r}
model_smpl$results
```

RSq: `r model_smpl$results$Rsquared`

RMSE: `r model_smpl$results$RMSE`

MAE:  `r model_smpl$results$MAE`


```{r}
df %>% head()
```

### df transform vars

```{r}
df_transfrm <- df %>% 
  select(sales:Radio)

df_transfrm
```

#### alpha,beta const

```{r}
alpha1 = .1
alpha2 = .1
alpha3 = .1

beta1 = .1
beta2 = .1
beta3 = .1
```


```{r}
df_transfrm <- df_transfrm %>% 
  mutate(FB_transfrm = FB^alpha1,
         FB_transfrm = if_else(row_number() == 1, 
                               FB^alpha1,
                               ( (FB + lag(FB_transfrm)*beta1)^alpha1 )
                               ) ,
         
         TV_transfrm = TV^alpha2,
         TV_transfrm = if_else(row_number() == 1, 
                               TV^alpha2,
                               ( (TV + lag(TV_transfrm)*beta2)^alpha2 )
                               )  ,
         
         Radio_transfrm = Radio^alpha3,
         Radio_transfrm = if_else(row_number() == 1, 
                               Radio^alpha3,
                               ( (Radio + lag(Radio_transfrm)*beta3)^alpha3 )
                               ) 
         )

df_transfrm
```

#### df test

```{r}
df_test <- tribble(
 ~sales, ~var1, ~var2,
  22, 230.1,  37.8,
  10, 44.5,  39.3,
  9,  17.2,  45.9,
  19, 151.5,  41.3,
  13, 180.8,  10.8,
  7,  8.7,    48.9,
  12, 57.5,   32.8,
  13, 120.2,  19.6,
  5,  8.6,    2.1,
  11, 199.8,  2.6)

df_test
```

```{r}
df_test  <- df_test %>% 
  mutate(var1_transfrm = var1^alpha1,
         var1_transfrm = if_else(row_number() == 1, 
                               var1^alpha1,
                               ( (var1 + lag(var1_transfrm)*beta1)^alpha1 )
                               ) ,
         
         var2_transfrm = var2^alpha2,
         var2_transfrm = if_else(row_number() == 1, 
                               var2^alpha2,
                               ( (var2 + lag(var2_transfrm)*beta2)^alpha2 )
                               ) 
         )

df_test
```

#### df test regr

```{r}
first_model <- lm(sales ~ var1_transfrm + var2_transfrm, data = df_test)

summary(first_model)
```

```{r}
first_model <- caret::train(form = sales ~ var1_transfrm + var2_transfrm, 
                            data = df_test,
                            method = "lm")

summary(first_model)
```


```{r}
first_model$results
```

```{r}
first_model$results$Rsquared
```

### alpha beta simulations

#### alpha beta comb.

```{r}
simulations <- crossing(alpha1 = seq(0.1,1,0.2),
         beta1 = seq(0.1,1,0.2),
         alpha2 = seq(0.1,1,0.2),
         beta2 = seq(0.1,1,0.2),
         alpha3 = seq(0.1,1,0.2),
         beta3 = seq(0.1,1,0.2))

simulations
```

As we have created 15k + combinations so will create 15k + models below to find the best `alpha`, `beta` for var transformations.

```{r}
simulations <- crossing(alpha1 = seq(0,1,0.1),
         beta1 = seq(0,1,0.1),
         alpha2 = seq(0,1,0.1),
         beta2 = seq(0,1,0.1),
         alpha3 = .00009,
         beta3 = .00009)

simulations
```



#### df simulation

```{r}
df_simulation <- df %>% 
  select(sales:Radio)

df_simulation
```

#### Parallel & lm function

```{r}
library(parallel)
library(doParallel)

no_cores <- parallel::detectCores() - 2
  #Leave one core available for Operating system

  cluster <- makePSOCKcluster(no_cores)
  registerDoParallel(cluster)
  
  cat("Model amped and ready to go with:", no_cores, "cores. \n")
```

this will take around 100 mins = 2 hrs to run as it took 1 min to run just 156 rows

```{r}
df_results <- data.frame(
           RMSE = double(),
           Rsq = double(),
           MAE = double()
           )


for (loop_count in 1:nrow(simulations)){ # 2   
  if(loop_count %% 500 == 0) print(loop_count)
  
  ##################################################################################################
  
  # transform data vars & save as new dataframe
  df_model <- df_simulation %>% 
  mutate(FB_transfrm = FB^simulations[loop_count,"alpha1"]$alpha1,
         FB_transfrm = if_else(row_number() == 1, 
                               FB^simulations[loop_count,"alpha1"]$alpha1,
                               ( (FB +
                                    lag(FB_transfrm)*simulations[loop_count,"beta1"]$beta1)^simulations[loop_count,"alpha1"]$alpha1 )
                               ),
         
         TV_transfrm = TV^simulations[loop_count,"alpha2"]$alpha2,
         TV_transfrm = if_else(row_number() == 1, 
                               TV^simulations[loop_count,"alpha2"]$alpha2,
                               ( (TV +
                                    lag(TV_transfrm)*simulations[loop_count,"beta2"]$beta2)^simulations[loop_count,"alpha2"]$alpha2 )
                               ),
         
         Radio_transfrm = Radio^simulations[loop_count,"alpha3"]$alpha3,
         Radio_transfrm = if_else(row_number() == 1, 
                               Radio^simulations[loop_count,"alpha3"]$alpha3,
                               ( (Radio +
                                    lag(Radio_transfrm)*simulations[loop_count,"beta3"]$beta3)^simulations[loop_count,"alpha3"]$alpha3 )
                               )
         
         
         ) %>% 
    select(sales, FB_transfrm, TV_transfrm, Radio_transfrm)
  
  
  ##################################################################################################
  
  # set seed
  set.seed(2022)
  
  # create lm model using transformed vars
  fit_model <- caret::train(form = sales ~ ., 
                            data = df_model,
                            method = "lm")
  
  # print(summary(fit_model))
  # Rsq_val <- fit_model$results$Rsquared
  
  df_results <-  rbind(df_results,
                        fit_model$results %>% 
                        select(RMSE:MAE)
                        )
}

df_results
```


```{r}
## When you are done:
stopCluster(cluster)
```

### Results MAE, Rsq

```{r}
df_results %>% 
  mutate(row_num = row_number()) %>% 
  filter(Rsquared == max(Rsquared))
```


```{r}
df_results %>% 
  mutate(row_num = row_number()) %>% 
  arrange(desc(Rsquared))
```


```{r}
df_results %>% 
  mutate(row_num = row_number()) %>% 
  arrange(RMSE)
```


```{r}
df_results %>% 
  mutate(row_num = row_number()) %>% 
  arrange(MAE)
```

#### Best alpha, beta values

Selecting row_number 6808 from above

```{r}
row_selected <- df_results %>%
  mutate(row_num = row_number()) %>% 
  arrange(MAE) %>%
  head(1) %>% 
  pull(row_num)

row_selected
```


```{r}
simulations %>% 
  mutate(row_num = row_number()) %>% 
  filter(row_num == row_selected)
```

### Matrix

```{r}
matrix(c(5,10,1,3),nrow = 2)
```


```{r}
matrix(c(5,10,1,3),ncol = 2)
```

```{r}
paste(df$Radio,collapse = ",") 
```

```{r}
df_matrix <- matrix(c(230.1,44.5,17.2,151.5,180.8,8.7,57.5,120.2,8.6,199.8,66.1,214.7,23.8,97.5,204.1,195.4,67.8,281.4,69.2,147.3,218.4,237.4,13.2,228.3,62.3,262.9,142.9,240.1,248.8,70.6,
         
         37.8,39.3,45.9,41.3,10.8,48.9,32.8,19.6,2.1,2.6,5.8,24,35.1,7.6,32.9,47.7,36.6,39.6,20.5,23.9,27.7,5.1,15.9,16.9,12.6,3.5,29.3,16.7,27.1,16,
         
         69.2,45.1,69.3,58.5,58.4,75,23.5,11.6,1,21.2,24.2,4,65.9,7.2,46,52.9,114,55.8,18.3,19.1,53.4,23.5,49.6,26.2,18.3,19.5,12.6,22.9,22.9,40.8), ncol = 3)

df_matrix
```



