---
title: "Assignment 1st look"
output: 
  html_notebook:
    highlight: tango
    df_print: paged
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
    number_sections: true
    toc_depth: 6

---

## Lib & Data

```{r}
library(tidyverse)
library(glue)
library(skimr)
library(naniar)
library(lubridate)
library(scales)
library(GGally)
```


```{r}
options(scipen = 999)
```


```{r}
df1 <- read_csv("Assessment-Data Scientist/DataScientistAssessment (1)/data_20160405.csv")

df1
```

```{r}
df1 <- df1 %>% 
  select(accID: last_col())

df1
```

## Data Prep & EDA

```{r}
summary(df1)
```

### missing data

```{r}
naniar::gg_miss_var(df1)
```

```{r}
skimr::skim(df1)
```

### Vars Cardinality

```{r}
# checking count of unique values in each variable 
df1 %>% map_df(n_unique)
```



```{r}
# checking variables with count of unique values less than 20
df1 %>% 
  map_df(n_unique) %>% 
  pivot_longer(cols = dplyr::everything(),
               names_to = "vars", 
               values_to = "distinct_count",) %>% 
  filter(distinct_count < 20)
```

```{r}
# data distribution by accType
df1$accType %>% table()
```

```{r}
# data distribution by distict
df1$district %>% table()
```

```{r}
# data distribution by salesVisit5
df1$salesVisit5 %>% table()
```

```{r}
# data distribution by compBrand
df1$compBrand %>% table()
```

#### Vars to factor

converting character & low cardinality variables to factors


```{r}
df1 <- df1 %>% 
  mutate(across(.cols = c(accType, district, compBrand), .fns = factor))

df1
```

### Adding date vars

```{r}
df1 <- df1 %>% 
  mutate(month_only = lubridate::month(month, abbr = T, label = T),
         month_only = factor(month_only, levels = month.abb),
         year_only = factor(lubridate::year(month))) %>% 
  
  select(accID, year_only, month_only, month, dplyr::everything())

df1
```

### Exploration

#### Correlation Plot

```{r fig.width=6, fig.height=6}
df1 %>% 
  select_if(is.numeric) %>% 
  cor() %>% 
  corrplot::corrplot(method = "number")
```

#### Other EDA

data distribution for accTYpe & Brand

```{r}
# data distribution for accTYpe & Brand
prop.table(table(df1$accType, df1$compBrand))
```

data distribution for accTYpe & Brand in %

```{r}
# data distribution for accTYpe & Brand in %
prop.table(table(df1$accType, df1$compBrand)) * 100
```

From above, Seems like we have lot more data for **Comp Brand 4**. 

Below, summarising some imp numeric vars by brand, year & account type

```{r}
# summarising some imp numeric vars by brand, year & account type 
df1 %>% 
  group_by(compBrand, year_only, accType) %>% 
  summarise_at(c("accSize", "accTargets", "qty"), sum, na.rm = T)
```

summarising accountsize by year & account type for Comp Brand 4

```{r}
# summarising accountsize by year & account type for Comp Brand 4
df1 %>% 
  group_by(compBrand, year_only, accType) %>% 
  summarise_at(c("accSize", "accTargets", "qty"), sum, na.rm = T) %>% 
  
  filter(compBrand == "4") %>% 
  
  ggplot(aes(x = accType, y = accSize, fill = accType)) +
  geom_col() +
  facet_wrap(~year_only) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(title = "Account Size for each Account type yearly (For Comp Brand 4)")
```

Account Size for each Account type yearly (For all Brands)

```{r}
df1 %>% 
  group_by(year_only, accType) %>% 
  summarise_at(c("accSize", "accTargets", "qty"), sum, na.rm = T) %>% 
  
  # filter(compBrand == "4") %>% 
  
  ggplot(aes(x = accType, y = accSize, fill = accType)) +
  geom_col() +
  facet_wrap(~year_only) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(title = "Account Size for each Account type yearly (For all Brands)")
```

Above, account size remains same for 2013 & 2014 but changes in 2015 when All Brands are used

Below, Total account size by months across years 

```{r}
# Total account size by months across years 
df1 %>% 
  arrange(month) %>% 
  group_by(year_only, month_only) %>% 
  summarise(accSize = sum(accSize), .groups = "drop") %>% 
  pivot_wider(id_cols = month_only, names_from = year_only, values_from = accSize) %>% 
  arrange(month_only)
```

Above, total account Size remains same for all the months.

Below, Total account Target by months across years 

```{r}
# Total account Target by months across years 
df1 %>% 
  arrange(month) %>% 
  group_by(year_only, month_only) %>% 
  summarise(accTargets = sum(accTargets), .groups = "drop") %>% 
  pivot_wider(id_cols = month_only, names_from = year_only, values_from = accTargets) %>% 
  arrange(month_only)
```

Above, Account Target remains same across the years

Below, Total sales by months & years

```{r}
# Total sales by months & years
df1 %>% 
  arrange(month) %>% 
  group_by(year_only, month_only) %>% 
  summarise(sales = sum(sales), .groups = "drop") %>% 
  pivot_wider(id_cols = month_only, names_from = year_only, values_from = sales) %>% 
  arrange(month_only)
```

Below, Total sales by months & years for Comp Brand 4 only

```{r}
# Total sales by months & years for Comp Brand 4 only
df1 %>% filter(compBrand == 4) %>% 
  arrange(month) %>% 
  group_by(year_only, month_only) %>% 
  summarise(sales = sum(sales), .groups = "drop") %>% 
  pivot_wider(id_cols = month_only, names_from = year_only, values_from = sales) %>% 
  arrange(month_only)
```

Above, seems like sales of Comp Brand 4 stopped from Jun'2015 onward & Brand 5 started from that period

Below, Total Sales timeline by Comp Brand type

```{r}
df1 %>%
  arrange(month) %>% 
  group_by(compBrand, month) %>% 
  summarise(sales = sum(sales), .groups = "drop") %>% 
  
  ggplot(aes(x = month, y = sales, group = compBrand, col = compBrand)) +
  geom_line() +
  theme_bw() +
  labs(title = "Total Sales timeline by Comp Brand type")
```

Above, Brand 5 started selling from 2015 only & same time Brand 4 stopped selling

Below, Checking data for Comp Brand 5

```{r}
df1 %>% 
  filter(compBrand == 5) %>% 
  arrange(month)
```

Below, Yearly Growth of Total Sales by Account type

```{r}
df1 %>% 
  arrange(month) %>% 
  group_by(year_only, accType) %>% 
  summarise(total_sales = sum(sales), .groups = "drop") %>% 
  
  ggplot(aes(x = year_only, y = total_sales, fill = accType)) +
  geom_col() +
  facet_wrap(~accType) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Yearly Growth of Total Sales by Account type")
```


Above, except `Private` all other account types have more sales in 2015 in comparison to historical years

Below, Growth of Total Sales by Account type (for Comp Brand 4)

```{r}
df1 %>% filter(compBrand == 4) %>% 
  arrange(month) %>% 
  group_by(year_only, accType) %>% 
  summarise(total_sales = sum(sales), .groups = "drop") %>% 
  
  ggplot(aes(x = year_only, y = total_sales, fill = accType)) +
  geom_col() +
  facet_wrap(~accType) +
  labs(title = "Growth of Total Sales by Account type (for Comp Brand 4)") +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6))
```

Above, for compBrand 4 - only `Polyclinic` has more sales in 2015 in comparison to historical years

Below, Sales Distribution by Comp Brand type

```{r}
# checking for sales outlier by brand 
df1 %>% 
  ggplot(aes(x = compBrand, y = sales)) +
  geom_boxplot() +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Sales Distribution by Comp Brand type")
```

Below, Sales Distribution by Comp Brand type based on Time Variable

```{r fig.width=8, fig.height=8}
df1 %>% 
  ggplot(aes(x = compBrand, y = sales)) +
  geom_boxplot() +
  facet_wrap(year_only~month_only) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Sales Distribution by Comp Brand type based on Year & Month")
```

Below, Monthly Sales Pattern each Year

```{r}
df1 %>% 
  group_by(year_only, month_only) %>% 
  summarise(sales = sum(sales, na.rm = T), .groups = "drop") %>% 
  
  ggplot(aes(x = month_only, y = sales, group = year_only, col = year_only)) +
  geom_line() +
  labs(title = "Monthly Sales Pattern each Year") +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6))
```

Below, Checking for Relation ship & patterns from multiple variables using pair plots 

```{r fig.width=8, fig.height=8}
df1 %>% 
  select(sales, qty,  year_only, accType, compBrand) %>% 
  ggpairs(aes(col = compBrand), progress = FALSE) +
  theme(axis.text.x = element_text(angle = 90))
```

From above:

1. Average Sales & Averaage qty sold overall of Brand 5 is higher than Brand 4 in all Account Types. This could probably be due to rising trend and Brand 5 being latest shows high values in all.

2. In 2015 Average Sales & Averaage qty sold of Brand 5 is higher than Brand 4 

3. Qty has very high correlation with Sales which is expected.



Below, Checking for Relation ship & patterns from multiple variables using pair plots

```{r fig.width=8, fig.height=8}
df1 %>% 
  select(sales, qty, strategy1, strategy2, strategy3, year_only, accType, compBrand) %>% 
  ggpairs(aes(col = compBrand), progress = FALSE) +
  theme(axis.text.x = element_text(angle = 90))
```

From above, Strategy 2 has some correlation with sales & qty 

Below, Checking date range for Comp Brand 4

```{r fig.width=8, fig.height=8}
df1 %>% 
  filter(compBrand == 4) %>% 
  arrange(month) %>% 
  select(month) %>%  
  summary()
```


```{r}
df1 %>%  
  ggplot(aes(x = strategy1, y = sales)) +
  geom_point() + geom_smooth(method = "lm", se = F) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Strategy1 Impact on Sales by Linear Regression")
```


```{r}
df1 %>%  
  filter(strategy1 != 0) %>% 
  ggplot(aes(x = strategy1, y = sales)) +
  geom_point() + geom_smooth(method = "lm", se = F) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Strategy1 Impact on Sales by Linear Regression for only Non 0 Strategy1 input")
```

```{r}
df1 %>% 
  ggplot(aes(x = strategy2, y = sales)) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  geom_point() + geom_smooth(method = "lm", se = F) +
  labs(title = "Strategy2 Impact on Sales by Linear Regression")
```

```{r}
df1 %>% 
  ggplot(aes(x = strategy3, y = sales)) +
  geom_point() + 
  geom_smooth(method = "lm", se = F) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Strategy1 Impact on Sales by Linear Regression for only Non 0 Strategy1 input")
```

```{r fig.width=7, fig.height=5}
df1 %>% 
  pivot_longer(cols = strategy1:strategy3, names_to = "stratergy_type", values_to = "expense") %>% 
  ggplot(aes(x = expense, y = sales, col = stratergy_type)) +
  geom_point(alpha = .5) +
  geom_smooth(method = "lm", se = F) +
  theme_bw() +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Impact of Strategies on Sales by Linear Regression")
  
```

```{r fig.width=7, fig.height=5}
df1 %>% 
  pivot_longer(cols = strategy1:strategy3, names_to = "stratergy_type", values_to = "expense") %>% 
  ggplot(aes(x = expense, y = sales, col = stratergy_type)) +
  geom_point(alpha = .5) +
  geom_smooth(se = F) +
  theme_bw() +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Impact of Strategies on Sales by Regression")
```

```{r}
df1 %>% 
  pivot_longer(cols = strategy1:strategy3, names_to = "stratergy_type", values_to = "expense") %>% 
  filter(stratergy_type == "strategy1")
```


```{r fig.width=7, fig.height=5}
df1 %>% 
  pivot_longer(cols = strategy1:strategy3, names_to = "stratergy_type", values_to = "expense") %>% 
  ggplot(aes(x = month, y = sales, col = stratergy_type)) +
  geom_jitter(alpha = .7) +
  # geom_smooth(method = 'lm') +
  theme_bw()
```

```{r}
df1 %>% 
  ggplot(aes(x = strategy1, y = sales, col = compBrand)) +
  geom_point() +
  geom_smooth() + 
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Strategy1 Impact on Sales by Regression")
```

Above plot, Strategy 1 for Brand 5 is showing Diminishing Returns and it attained peak around 800k-900k strategy1.


```{r}
df1 %>% 
  ggplot(aes(x = strategy2, y = sales, col = compBrand)) +
  geom_point() +
  geom_smooth() +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Strategy2 Impact on Sales by Regression")
```

Above plot, 

Strategy 2 for Brand 5 is showing Diminishing Returns and it attained peak around 1Mn -1.1Mn strategy2.

Strategy 2 for Brand 4 doesn't show as much elasticity as in Brand 4 but still growth remains constant & doesnt peak before end.


```{r}
df1 %>% 
  filter(strategy2 != 0) %>% 
  ggplot(aes(x = strategy2, y = sales, col = compBrand)) +
  geom_point() +
  geom_smooth() +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Strategy2 Impact on Sales by Regression with only Non 0 Strategy2 inputs")
```



```{r}
df1 %>% 
  ggplot(aes(x = strategy3, y = sales, col = compBrand)) +
  geom_point() +
  geom_smooth() +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Strategy3 Impact on Sales by Regression")
```

Above plot, Strategy 3 doesn't seems to make much of difference in driving sales as majority of it as 0 strategy value.


```{r}
df1 %>% 
  filter(strategy3 != 0) %>% 
  ggplot(aes(x = strategy3, y = sales, col = compBrand)) +
  geom_point() +
  geom_smooth() +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Strategy3 Impact on Sales by Regression with only Non 0 strategy3 inputs")
```


```{r}
df1 %>% 
  filter(strategy3 != 0) %>% 
  ggplot(aes(x = strategy3, y = sales, col = compBrand)) +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Strategy3 Impact on Sales by Linear Regr. with only Non 0 strategy3 inputs")
```

Above plot, Strategy 3 makes good imapct on driving sales for Brand 4 when Strategy 3 is non 0.

Checking for Account ID below

```{r}
df1$accID %>% table()
```

```{r}
df1 %>% 
  filter(compBrand == 5) %>% 
  pull(accID) %>% 
  table()
```


```{r fig.width=8, fig.height=6}
df1 %>% 
  group_by(accID) %>% 
  summarise(sales = sum(sales, na.rm = T), .groups = "drop") %>% 
  arrange(desc(sales)) %>% 
  head(70) %>% 
  
  ggplot(aes(x = fct_reorder(accID, sales, max), y = sales)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Total Sales by top 70 Account ID", 
       x = "Account ID") +
  coord_flip()
```

#### Lin. Regression Plots


```{r fig.width=8, fig.height=6}
df1 %>% 
  pivot_longer(cols = strategy1:salesVisit5, 
               names_to = "marketing_channel", values_to = "spend") %>% 
  ggplot(aes(x = spend, y = sales, col = accType)) +
  geom_point(alpha = .6) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~marketing_channel) +
  scale_x_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Marketing Spend to Sales with Linear Regr. by Each Strategy & visit type")
```

Above plot,

1. Most Spend values comes from salesVisit1  to 3 in Pharmacy account Type

2. Strategy 1 & 2 shows best Return on Investment in Pharmacy



```{r fig.width=8, fig.height=6}
df1 %>% 
  
  select(month,accType, sales:salesVisit5) %>% 
  group_by(month,accType) %>% 
  summarise_at(vars(sales:salesVisit5), sum, na.rm = TRUE) %>% 
  
  pivot_longer(cols = strategy1:salesVisit5, 
               names_to = "marketing_channel", values_to = "spend") %>% 
  ggplot(aes(x = spend, y = sales, col = accType)) +
  geom_point(alpha = .6) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~marketing_channel) +
  scale_x_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Summarised Monthly Marketing Spend to Sales by Each Strategy & visit type")
```




```{r fig.width=8, fig.height=6}
df1 %>% 
  pivot_longer(cols = strategy1:salesVisit5, 
               names_to = "marketing_channel", values_to = "spend") %>% 
  ggplot(aes(x = spend, y = sales, col = marketing_channel)) +
  geom_point(alpha = .6) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~accType) +
  scale_x_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Marketing Spend to Sales for each Marketing type with Linear Regr. by Account type")
```



```{r fig.width=8, fig.height=6}
df1 %>% 
  select(month,accType, sales:salesVisit5) %>% 
  group_by(month,accType) %>% 
  summarise_at(vars(sales:salesVisit5), sum, na.rm = TRUE) %>% 
  
  pivot_longer(cols = strategy1:salesVisit5, 
               names_to = "marketing_channel", values_to = "spend") %>% 
  ggplot(aes(x = spend, y = sales, col = marketing_channel)) +
  geom_point(alpha = .6) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~accType) +
  scale_x_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = " Monthly Summarised Marketing Spend to Sales for each Marketing type by Account type")
```


From Above, we may need to build Different Models for different Account Type as the effect of different marketing spends behave little different depending on Account type.

#### Non Lin. Regression Plots


```{r fig.width=8, fig.height=6}
df1 %>% 
  pivot_longer(cols = strategy1:salesVisit5, 
               names_to = "marketing_channel", values_to = "spend") %>% 
  ggplot(aes(x = spend, y = sales, col = accType)) +
  geom_point(alpha = .6) +
  geom_smooth(se = FALSE) +
  facet_wrap(~marketing_channel) +
  scale_x_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Marketing Spend to Sales with Linear Regr. by Each Strategy & visit type")
```


```{r fig.width=8, fig.height=6, warning=FALSE}
df1 %>% 
  
  select(month,accType, sales:salesVisit5) %>% 
  group_by(month,accType) %>% 
  summarise_at(vars(sales:salesVisit5), sum, na.rm = TRUE) %>% 
  
  pivot_longer(cols = strategy1:salesVisit5, 
               names_to = "marketing_channel", values_to = "spend") %>% 
  ggplot(aes(x = spend, y = sales, col = accType)) +
  geom_point(alpha = .6) +
  geom_smooth(se = FALSE) +
  facet_wrap(~marketing_channel) +
  scale_x_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Summarised Monthly Marketing Spend to Sales by Each Strategy & visit type")
```



```{r fig.width=8, fig.height=6}
df1 %>% 
  pivot_longer(cols = strategy1:salesVisit5, 
               names_to = "marketing_channel", values_to = "spend") %>% 
  ggplot(aes(x = spend, y = sales, col = marketing_channel)) +
  geom_point(alpha = .6) +
  geom_smooth(se = FALSE, formula = y ~ s(x, bs = "cs", k=3)) +
  facet_wrap(~accType) +
  scale_x_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = "Marketing Spend to Sales for each Marketing type with Linear Regr. by Account type")
```

Above plot shows the Saturation in the Sales on various Marketing channel Spends 


```{r fig.width=8, fig.height=6}
df1 %>% 
  select(month,accType, sales:salesVisit5) %>% 
  group_by(month,accType) %>% 
  summarise_at(vars(sales:salesVisit5), sum, na.rm = TRUE) %>% 
  
  pivot_longer(cols = strategy1:salesVisit5, 
               names_to = "marketing_channel", values_to = "spend") %>% 
  ggplot(aes(x = spend, y = sales, col = marketing_channel)) +
  geom_point(alpha = .6) +
  geom_smooth(se = FALSE, span = 0.9) +
  facet_wrap(~accType) +
  scale_x_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  scale_y_continuous(labels = unit_format(unit = "Mn", scale = 1e-6)) +
  labs(title = " Monthly Summarised Marketing Spend to Sales for each Marketing type by Account type")
```





