---
title: "Part 2 to trnsfm & build model with adstock, diminishing ret"
output: 
  html_notebook:
    highlight: tango
    df_print: paged
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
    number_sections: false
    toc_depth: 6
---

```{r}
library(tidyverse)
library(lubridate)
library(caret)
library(stargazer) # to view combine regression results
```

### Best alpha, betas

based on MAE & decent Rsq

```{r}
simulations %>% 
  mutate(row_num = row_number()) %>% 
  filter(row_num == row_selected)
```

#### alpha,beta const

```{r}
alpha1 = .4
alpha2 = .6
alpha3 = 9e-05

beta1 = 1
beta2 = .1
beta3 = 9e-05
```

```{r}
df_transfrm_applied <- df_transfrm %>% 
  mutate(FB_transfrm = FB^alpha1,
         FB_transfrm = if_else(row_number() == 1, 
                               FB^alpha1,
                               ( (FB + lag(FB_transfrm)*beta1)^alpha1 )
                               ) ,
         
         TV_transfrm = TV^alpha2,
         TV_transfrm = if_else(row_number() == 1, 
                               TV^alpha2,
                               ( (TV + lag(TV_transfrm)*beta2)^alpha2 )
                               )  ,
         
         Radio_transfrm = Radio^alpha3,
         Radio_transfrm = if_else(row_number() == 1, 
                               Radio^alpha3,
                               ( (Radio + lag(Radio_transfrm)*beta3)^alpha3 )
                               ) 
         )

df_transfrm_applied
```

```{r}
df_transfrm_applied %>% 
  ggplot(aes(x = FB, y = FB_transfrm)) +
  geom_point() +
  theme_bw()
```

### 1. Model

```{r}
set.seed(2022)

lm(sales ~ FB_transfrm+TV_transfrm+Radio_transfrm,
   data = df_transfrm_applied) %>%
  summary()
```

```{r}
set.seed(2022)

caret::train(form = sales ~ FB_transfrm+TV_transfrm+Radio_transfrm,
   data = df_transfrm_applied, method = "lm")$results 
```

```{r}
set.seed(2022)

caret::train(form = sales ~ FB_transfrm+TV_transfrm,
   data = df_transfrm_applied, method = "lm")$results 

```

```{r}
set.seed(2022)

model_applied <- caret::train(form = sales ~ FB_transfrm+TV_transfrm+Radio_transfrm,
   data = df_transfrm_applied, method = "lm") 

model_applied
```

```{r}
stargazer(model_applied$finalModel,type="text") 
```

```{r}
stargazer(lm(sales ~ FB_transfrm+TV_transfrm+Radio_transfrm,
   data = df_transfrm_applied),type="text")
```


```{r}
model_applied$results
```

```{r}
predctn_model_transm <- predict(model_applied, data = df_transfrm_applied)
predctn_model_transm
```

```{r}
mean(abs(df_transfrm_applied$sales-predctn_model_transm))
```

```{r}
df_results_applied <- data.frame(cbind(sales = df_transfrm_applied$sales, 
                                       predctn_model_transm,
                                       predctn_model_smpl)
                                 )

df_results_applied
```

```{r}
df_results_applied %>% 
  mutate(week_num = row_number()) %>% 
  pivot_longer(cols = sales:predctn_model_smpl, names_to = "sales_type", values_to = "count") %>% 
  ggplot(aes(x = week_num, y = count, group = sales_type, col = sales_type)) +
  geom_line(size = 1, alpha = .6) +
  theme_bw() +
  theme(legend.position = "top")
```

```{r}
df_model_coeff <- model_applied$finalModel$coefficients %>% 
  data.frame() %>% rownames_to_column() %>% 
  rename(coeff_name = rowname,
         coeff_value = '.')

df_model_coeff
```

```{r}
df_transfrm_applied %>%
  pivot_longer(cols = c(FB_transfrm,TV_transfrm,Radio_transfrm),
               names_to = "sales_channel", values_to = "sales_num") %>% 
  ggplot(aes(x = sales_num, y = sales, col = sales_channel, group = 1)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

Above graph is not treating linear regression as multivariate but it is treating it as a single var Regression

#### Forecast Sales

```{r}
df_sales_forecast <- 
  df_transfrm_applied %>% 
  mutate(time_week = row_number()) %>% 
  select(time_week, sales, FB_transfrm:Radio_transfrm) %>% 
  mutate(FB_sales_forecast = FB_transfrm * (df_model_coeff %>% filter(coeff_name == "FB_transfrm"))$coeff_value,
         TV_sales_forecast = TV_transfrm * (df_model_coeff %>% filter(coeff_name == "TV_transfrm"))$coeff_value,
         Radio_sales_forecast = Radio_transfrm * (df_model_coeff %>% filter(coeff_name == "Radio_transfrm"))$coeff_value,
         Baseline = (df_model_coeff %>% filter(coeff_name == "(Intercept)"))$coeff_value) %>% 
   mutate(sales_forecast = rowSums(.[,c("FB_sales_forecast","TV_sales_forecast","Radio_sales_forecast","Baseline")])  )  
df_sales_forecast
```

#### df Sales contrib

```{r}
df_sales_forecast %>% 
  summarise(sales = sum(sales,na.rm = T),
            FB_contrib = sum(FB_sales_forecast, na.rm = T),
            TV_contrib = sum(TV_sales_forecast, na.rm = T),
            Radio_contrib = sum(Radio_sales_forecast, na.rm = T),
            Baseline_contrib = sum(Baseline, na.rm = T),) %>% 
  mutate(total = rowSums(.[,c(2:5)] )) %>% 
  mutate(FB_contrib_perc = FB_contrib/total * 100,
         TV_contrib_perc = TV_contrib/total * 100,
         Radio_contrib_perc = Radio_contrib/total * 100,
         Baseline_contrib_perc = Baseline_contrib/total * 100)
```

#### vif

```{r}
library(car)
```

from: https://stackoverflow.com/questions/64592303/how-to-use-vif-in-r

```{r}
vif(model_applied$finalModel)
```

```{r}
set.seed(2022)

vif(lm(sales ~ FB_transfrm+TV_transfrm+Radio_transfrm,
   data = df_transfrm_applied))
```

#### DW Test for Autocorelatiom

```{r}
car::durbinWatsonTest(model_applied$finalModel)
```

AS the `p-value > .05` so there is **no autocorrelation** in the model.

#### Residuals Dist. check

```{r}
hist(df_transfrm_applied$sales-predctn_model_transm)
```



### 2. Model w/o Radio

```{r}
df_transfrm_applied2 <- df_transfrm %>% 
  mutate(FB_transfrm = FB^alpha1,
         FB_transfrm = if_else(row_number() == 1, 
                               FB^alpha1,
                               ( (FB + lag(FB_transfrm)*beta1)^alpha1 )
                               ) ,
         
         TV_transfrm = TV^alpha2,
         TV_transfrm = if_else(row_number() == 1, 
                               TV^alpha2,
                               ( (TV + lag(TV_transfrm)*beta2)^alpha2 )
                               )  ,
         
         Radio_transfrm = Radio^alpha3,
         Radio_transfrm = if_else(row_number() == 1, 
                               Radio^alpha3,
                               ( (Radio + lag(Radio_transfrm)*beta3)^alpha3 )
                               ) 
         )

df_transfrm_applied2
```

```{r}
set.seed(2022)

lm(sales ~ FB_transfrm+TV_transfrm,
   data = df_transfrm_applied2) %>% 
  summary()
```

```{r}
set.seed(2022)

lm(sales ~ FB_transfrm+TV_transfrm+Radio,
   data = df_transfrm_applied2) %>% 
  summary()
```

```{r}
set.seed(2022)

model_applied2 <- caret::train(form = sales ~ FB_transfrm+TV_transfrm,
   data = df_transfrm_applied2, method = "lm") 

model_applied2 %>% 
  summary()
```

```{r}
model_applied2$results
```

```{r}
predctn_model_transm2 <- predict(model_applied2, data = df_transfrm_applied2)
predctn_model_transm2
```

```{r}
df_results_applied2 <- data.frame(cbind(sales = df_transfrm_applied2$sales, 
                                       predctn_model_transm2,
                                       predctn_model_transm,
                                       predctn_model_smpl)
                                 )

df_results_applied2
```

```{r}
df_results_applied2 %>% 
  mutate(week_num = row_number()) %>% 
  pivot_longer(cols = sales:predctn_model_smpl, names_to = "sales_type", values_to = "count") %>% 
  ggplot(aes(x = week_num, y = count, group = sales_type, col = sales_type)) +
  geom_line(size = 1, alpha = .8) +
  theme_bw() +
  theme(legend.position = "top")
```

```{r}
model_applied2$finalModel$coefficients
```

```{r}
df_model_coeff2 <- model_applied2$finalModel$coefficients %>% 
  data.frame() %>% rownames_to_column() %>% 
  rename(coeff_name = rowname,
         coeff_value = '.')

df_model_coeff2
```

```{r}
df_transfrm_applied2 %>%
  pivot_longer(cols = c(FB_transfrm,TV_transfrm),
               names_to = "sales_channel", values_to = "sales_num") %>% 
  ggplot(aes(x = sales_num, y = sales, col = sales_channel, group = 1)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlim(c(0,11)) +
  ylim(c(0,25))
```

Above graph is not treating linear regression as multivariate but it is treating it as a single var Regression

### Forecast Sales

```{r}
df_sales_forecast2 <- 
  df_transfrm_applied2 %>% 
  mutate(time_week = row_number()) %>% 
  select(time_week, sales, FB_transfrm:Radio_transfrm) %>% 
  mutate(FB_sales_forecast = FB_transfrm * (df_model_coeff2 %>% filter(coeff_name == "FB_transfrm"))$coeff_value,
         TV_sales_forecast = TV_transfrm * (df_model_coeff2 %>% filter(coeff_name == "TV_transfrm"))$coeff_value,
         Radio_sales_forecast = Radio_transfrm * 0,
         Baseline = (df_model_coeff2 %>% filter(coeff_name == "(Intercept)"))$coeff_value) %>% 
   mutate(sales_forecast = rowSums(.[,c("FB_sales_forecast","TV_sales_forecast","Radio_sales_forecast","Baseline")])  )  
df_sales_forecast2
```

### df Sales contrib

```{r}
df_sales_forecast2 %>% 
  summarise(sales = sum(sales,na.rm = T),
            FB_contrib = sum(FB_sales_forecast, na.rm = T),
            TV_contrib = sum(TV_sales_forecast, na.rm = T),
            Radio_contrib = sum(Radio_sales_forecast, na.rm = T),
            Baseline_contrib = sum(Baseline, na.rm = T),) %>% 
  mutate(total = rowSums(.[,c(2:5)] )) %>% 
  mutate(FB_contrib_perc = FB_contrib/total * 100,
         TV_contrib_perc = TV_contrib/total * 100,
         Radio_contrib_perc = Radio_contrib/total * 100,
         Baseline_contrib_perc = Baseline_contrib/total * 100)
```

#### vif

```{r}
library(car)
```

```{r}
vif(model_applied2$finalModel)
```

```{r}
set.seed(2022)

vif(lm(sales ~ FB_transfrm+TV_transfrm,
   data = df_transfrm_applied2))
```


#### DW Test for Autocorelatiom

```{r}
car::durbinWatsonTest(model_applied2$finalModel)
```

AS the `p-value > .05` so there is **no autocorrelation** in the model.

#### Residuals Dist. check

```{r}
hist(df_transfrm_applied2$sales-predctn_model_transm2)
```



### 3. Model (Ridge)

```{r}
df_transfrm_applied3 <- df_transfrm %>% 
  mutate(FB_transfrm = FB^alpha1,
         FB_transfrm = if_else(row_number() == 1, 
                               FB^alpha1,
                               ( (FB + lag(FB_transfrm)*beta1)^alpha1 )
                               ) ,
         
         TV_transfrm = TV^alpha2,
         TV_transfrm = if_else(row_number() == 1, 
                               TV^alpha2,
                               ( (TV + lag(TV_transfrm)*beta2)^alpha2 )
                               )  ,
         
         Radio_transfrm = Radio^alpha3,
         Radio_transfrm = if_else(row_number() == 1, 
                               Radio^alpha3,
                               ( (Radio + lag(Radio_transfrm)*beta3)^alpha3 )
                               ) 
         )

df_transfrm_applied3
```

```{r}
set.seed(2022)

model_applied3 <-  caret::train(form = sales ~ FB_transfrm+TV_transfrm,
   data = df_transfrm_applied3, method = "ridge")

model_applied3
```

```{r}
model_applied3$modelInfo$parameters
```

```{r}
model_applied3$results
```

```{r}
set.seed(2022)

caret::train(form = sales ~ FB_transfrm+TV_transfrm+Radio_transfrm,
   data = df_transfrm_applied3, method = "ridge")
```

```{r}
predctn_model_transm3 <- predict(model_applied3, data = df_transfrm_applied3)
predctn_model_transm3
```

```{r}
df_results_applied3 <- data.frame(cbind(sales = df_transfrm_applied3$sales, 
                                       predctn_model_transm3,
                                       predctn_model_smpl)
                                 )

df_results_applied3
```

```{r}
df_results_applied3 %>% 
  mutate(week_num = row_number()) %>% 
  pivot_longer(cols = sales:predctn_model_smpl, names_to = "sales_type", values_to = "count") %>% 
  ggplot(aes(x = week_num, y = count, group = sales_type, col = sales_type)) +
  geom_line(size = 1, alpha = .6) +
  theme_bw() +
  theme(legend.position = "top")
```

```{r}
lambda_use <- min(model_applied3$finalModel$lambda[model_applied3$finalModel$lambda >= model_applied3$bestTune$lambda])

position <- which(model_applied3$finalModel$lambda == lambda_use)

data.frame(coef(model_applied3$finalModel)[, position])
```

**Imp**: `Ridge` regression reduces the coeff to 0 so there are no coeff above.

#### Residuals Dist. check

```{r}
hist(df_transfrm_applied3$sales-predctn_model_transm3)
```


### Model 3 ended above

### 4. Model (optim)

Using **optimized params** genereated in file [Optimizer Rmarkdown file](V:/1. R & Python work/3. R/Market Mix Models - Econometric/Adstock - diminishing in R/3. Attempting optim optimizer.Rmd)

#### Optim function call

```{r}
optim(par = c(.1,.1,.1,.1,.1,.1), # initiating a1=.1,a2=.1 & so on till b3=.1
      df_optim = df_optim,
      fn = replicate_excel_solver, 
      lower = c(.001,.001,.001,.001,.001,.001),
      upper = c(1,1,1,1,1,1),
      method = "L-BFGS-B")
```

#### alpha beta setting

```{r}
alpha1 = 0.3596438
alpha2 = 0.8996762
alpha3 = 0.0010000

beta1 = 1
beta2 = 0.0010000
beta3 = 0.0010000
```

```{r}
df_transfrm_applied4 <- df_transfrm %>% 
  mutate(FB_transfrm = FB^alpha1,
         FB_transfrm = if_else(row_number() == 1, 
                               FB^alpha1,
                               ( (FB + lag(FB_transfrm)*beta1)^alpha1 )
                               ) ,
         
         TV_transfrm = TV^alpha2,
         TV_transfrm = if_else(row_number() == 1, 
                               TV^alpha2,
                               ( (TV + lag(TV_transfrm)*beta2)^alpha2 )
                               )  ,
         
         Radio_transfrm = Radio^alpha3,
         Radio_transfrm = if_else(row_number() == 1, 
                               Radio^alpha3,
                               ( (Radio + lag(Radio_transfrm)*beta3)^alpha3 )
                               ) 
         )

df_transfrm_applied4
```

#### model

```{r}
set.seed(2022)

lm(sales ~ FB_transfrm+TV_transfrm,
   data = df_transfrm_applied4) %>% 
  summary()
```

```{r}
set.seed(2022)

lm(sales ~ FB_transfrm+TV_transfrm+Radio_transfrm,
   data = df_transfrm_applied4) %>% 
  summary()
```

```{r}
set.seed(2022)

model_applied4 <- caret::train(form = sales ~ FB_transfrm+TV_transfrm+Radio_transfrm,
   data = df_transfrm_applied4, method = "lm") 

model_applied4 %>% 
  summary()
```

```{r}
model_applied4$results
```

```{r}
predctn_model_transm4 <- predict(model_applied4, data = df_transfrm_applied4)
predctn_model_transm4
```

```{r}
df_results_applied4 <- data.frame(cbind(sales = df_transfrm_applied4$sales, 
                                       predctn_model_transm4,
                                       predctn_model_transm2,
                                       predctn_model_smpl)
                                 )

df_results_applied4
```

```{r}
df_results_applied4 %>% 
  mutate(week_num = row_number()) %>% 
  pivot_longer(cols = sales:predctn_model_smpl, names_to = "sales_type", values_to = "count") %>% 
  ggplot(aes(x = week_num, y = count, group = sales_type, col = sales_type)) +
  geom_line(size = 1, alpha = .8) +
  theme_bw() +
  theme(legend.position = "top")
```

```{r}
model_applied4$finalModel$coefficients
```

```{r}
df_model_coeff4 <- model_applied4$finalModel$coefficients %>% 
  data.frame() %>% rownames_to_column() %>% 
  rename(coeff_name = rowname,
         coeff_value = '.')

df_model_coeff4
```

#### Forecast Sales

```{r}
df_sales_forecast4 <- 
  df_transfrm_applied4 %>% 
  mutate(time_week = row_number()) %>% 
  select(time_week, sales, FB_transfrm:Radio_transfrm) %>% 
  mutate(FB_sales_forecast = FB_transfrm * (df_model_coeff4 %>% filter(coeff_name == "FB_transfrm"))$coeff_value,
         TV_sales_forecast = TV_transfrm * (df_model_coeff4 %>% filter(coeff_name == "TV_transfrm"))$coeff_value,
         Radio_sales_forecast = Radio_transfrm * (df_model_coeff4 %>% filter(coeff_name == "Radio_transfrm"))$coeff_value,
         Baseline = (df_model_coeff4 %>% filter(coeff_name == "(Intercept)"))$coeff_value) %>% 
   mutate(sales_forecast = rowSums(.[,c("FB_sales_forecast","TV_sales_forecast","Radio_sales_forecast","Baseline")])  )  

df_sales_forecast4
```

#### df Sales contrib

```{r}
df_sales_forecast4 %>% 
  summarise(sales = sum(sales,na.rm = T),
            FB_contrib = sum(FB_sales_forecast, na.rm = T),
            TV_contrib = sum(TV_sales_forecast, na.rm = T),
            Radio_contrib = sum(Radio_sales_forecast, na.rm = T),
            Baseline_contrib = sum(Baseline, na.rm = T),) %>% 
  mutate(total = rowSums(.[,c(2:5)] )) %>% 
  mutate(FB_contrib_perc = FB_contrib/total * 100,
         TV_contrib_perc = TV_contrib/total * 100,
         Radio_contrib_perc = Radio_contrib/total * 100,
         Baseline_contrib_perc = Baseline_contrib/total * 100)
```

#### vif

```{r}
library(car)
```

```{r}
vif(model_applied4$finalModel)
```

```{r}
set.seed(2022)

vif(lm(sales ~ FB_transfrm+TV_transfrm+Radio_transfrm,
   data = df_transfrm_applied4))
```


#### DW Test for Autocorelatiom

```{r}
car::durbinWatsonTest(model_applied4$finalModel)
```

AS the `p-value > .05` so there is **no autocorrelation** in the model.

#### Residuals Dist. check

```{r}
hist(df_transfrm_applied4$sales-predctn_model_transm4)
```

### 4.2 Model W/o Radio


#### alpha beta setting

```{r}
alpha1 = 0.3596438
alpha2 = 0.8996762
alpha3 = 0.0010000

beta1 = 1
beta2 = 0.0010000
beta3 = 0.0010000
```

```{r}
df_transfrm_applied4_2 <- df_transfrm %>% 
  mutate(FB_transfrm = FB^alpha1,
         FB_transfrm = if_else(row_number() == 1, 
                               FB^alpha1,
                               ( (FB + lag(FB_transfrm)*beta1)^alpha1 )
                               ) ,
         
         TV_transfrm = TV^alpha2,
         TV_transfrm = if_else(row_number() == 1, 
                               TV^alpha2,
                               ( (TV + lag(TV_transfrm)*beta2)^alpha2 )
                               )  ,
         
         Radio_transfrm = Radio^alpha3,
         Radio_transfrm = if_else(row_number() == 1, 
                               Radio^alpha3,
                               ( (Radio + lag(Radio_transfrm)*beta3)^alpha3 )
                               ) 
         )

df_transfrm_applied4_2
```

#### model


```{r}
set.seed(2022)

model_applied4_2 <- caret::train(form = sales ~ FB_transfrm+TV_transfrm,
   data = df_transfrm_applied4_2, method = "lm") 

model_applied4_2 %>% 
  summary()
```

```{r}
model_applied4_2$results
```

```{r}
predctn_model_transm4_2 <- predict(model_applied4_2, data = df_transfrm_applied4_2)
predctn_model_transm4_2
```

```{r}
df_results_applied4_2 <- data.frame(cbind(sales = df_transfrm_applied4_2$sales, 
                                       predctn_model_transm4_2,
                                       predctn_model_transm2,
                                       predctn_model_smpl)
                                 )

df_results_applied4_2
```

```{r}
df_results_applied4_2 %>% 
  mutate(week_num = row_number()) %>% 
  pivot_longer(cols = sales:predctn_model_smpl, names_to = "sales_type", values_to = "count") %>% 
  ggplot(aes(x = week_num, y = count, group = sales_type, col = sales_type)) +
  geom_line(size = 1, alpha = .8) +
  theme_bw() +
  theme(legend.position = "top")
```

```{r}
model_applied4_2$finalModel$coefficients
```

```{r}
df_model_coeff4_2 <- model_applied4_2$finalModel$coefficients %>% 
  data.frame() %>% rownames_to_column() %>% 
  rename(coeff_name = rowname,
         coeff_value = '.')

df_model_coeff4_2
```

#### Forecast Sales

```{r}
df_sales_forecast4_2 <- 
  df_transfrm_applied4 %>% 
  mutate(time_week = row_number()) %>% 
  select(time_week, sales, FB_transfrm:Radio_transfrm) %>% 
  mutate(FB_sales_forecast = FB_transfrm * (df_model_coeff4_2 %>% filter(coeff_name == "FB_transfrm"))$coeff_value,
         TV_sales_forecast = TV_transfrm * (df_model_coeff4_2 %>% filter(coeff_name == "TV_transfrm"))$coeff_value,
         Radio_sales_forecast = Radio_transfrm * 0,
         Baseline = (df_model_coeff4_2 %>% filter(coeff_name == "(Intercept)"))$coeff_value) %>% 
   mutate(sales_forecast = rowSums(.[,c("FB_sales_forecast","TV_sales_forecast","Radio_sales_forecast","Baseline")])  )  

df_sales_forecast4_2
```

#### df Sales contrib

```{r}
df_sales_forecast4_2 %>% 
  summarise(sales = sum(sales,na.rm = T),
            FB_contrib = sum(FB_sales_forecast, na.rm = T),
            TV_contrib = sum(TV_sales_forecast, na.rm = T),
            Radio_contrib = sum(Radio_sales_forecast, na.rm = T),
            Baseline_contrib = sum(Baseline, na.rm = T),) %>% 
  mutate(total = rowSums(.[,c(2:5)] )) %>% 
  mutate(FB_contrib_perc = FB_contrib/total * 100,
         TV_contrib_perc = TV_contrib/total * 100,
         Radio_contrib_perc = Radio_contrib/total * 100,
         Baseline_contrib_perc = Baseline_contrib/total * 100)
```

#### vif

```{r}
library(car)
```

```{r}
vif(model_applied4_2$finalModel)
```


#### DW Test for Autocorelatiom

```{r}
car::durbinWatsonTest(model_applied4_2$finalModel)
```

AS the `p-value > .05` so there is **no autocorrelation** in the model.

#### Residuals Dist. check

```{r}
hist(df_transfrm_applied4_2$sales-predctn_model_transm4_2)
```


### Inspection

```{r}
df_transfrm_applied4 %>% 
  ggplot(aes(x = Radio_transfrm, y = sales)) +
  geom_point() +
  theme_bw()
```

```{r}
df_transfrm_applied4 %>% 
  ggplot(aes(x = FB_transfrm, y = sales)) +
  geom_point() +
  theme_bw()
```


```{r}
df_transfrm_applied4 %>% 
  ggplot(aes(x = TV_transfrm, y = sales)) +
  geom_point() +
  theme_bw()
```


### 5. Model Center,Scale


#### alpha beta setting

```{r}
alpha1 = 0.3596438
alpha2 = 0.8996762
alpha3 = 0.0010000

beta1 = 1
beta2 = 0.0010000
beta3 = 0.0010000
```

```{r}
df_transfrm_applied5 <- df_transfrm %>% 
  mutate(FB_transfrm = FB^alpha1,
         FB_transfrm = if_else(row_number() == 1, 
                               FB^alpha1,
                               ( (FB + lag(FB_transfrm)*beta1)^alpha1 )
                               ) ,
         
         TV_transfrm = TV^alpha2,
         TV_transfrm = if_else(row_number() == 1, 
                               TV^alpha2,
                               ( (TV + lag(TV_transfrm)*beta2)^alpha2 )
                               )  ,
         
         Radio_transfrm = Radio^alpha3,
         Radio_transfrm = if_else(row_number() == 1, 
                               Radio^alpha3,
                               ( (Radio + lag(Radio_transfrm)*beta3)^alpha3 )
                               ) 
         )

df_transfrm_applied5
```

#### model

```{r}
set.seed(2022)

model_applied5 <- caret::train(form = sales ~ FB_transfrm+TV_transfrm+Radio_transfrm,
   data = df_transfrm_applied5, 
   method = "lm",
   preProcess = c("center","scale")) 

model_applied5 %>% 
  summary()
```

```{r}
model_applied5$results
```

```{r}
predctn_model_transm5 <- predict(model_applied5, data = df_transfrm_applied5)
predctn_model_transm5
```

```{r}
df_results_applied5 <- data.frame(cbind(sales = df_transfrm_applied5$sales, 
                                       predctn_model_transm5,
                                       predctn_model_transm2,
                                       predctn_model_smpl)
                                 )

df_results_applied5
```

```{r}
df_results_applied5 %>% 
  mutate(week_num = row_number()) %>% 
  pivot_longer(cols = sales:predctn_model_smpl, names_to = "sales_type", values_to = "count") %>% 
  ggplot(aes(x = week_num, y = count, group = sales_type, col = sales_type)) +
  geom_line(size = 1, alpha = .8) +
  theme_bw() +
  theme(legend.position = "top")
```

```{r}
model_applied5$finalModel$coefficients
```

```{r}
df_model_coeff5 <- model_applied5$finalModel$coefficients %>% 
  data.frame() %>% rownames_to_column() %>% 
  rename(coeff_name = rowname,
         coeff_value = '.')

df_model_coeff5
```

#### Forecast Sales

```{r}
df_sales_forecast5 <- 
  df_transfrm_applied5 %>% 
  mutate(time_week = row_number()) %>% 
  select(time_week, sales, FB_transfrm:Radio_transfrm) %>% 
  mutate(FB_sales_forecast = FB_transfrm * (df_model_coeff5 %>% filter(coeff_name == "FB_transfrm"))$coeff_value,
         TV_sales_forecast = TV_transfrm * (df_model_coeff5 %>% filter(coeff_name == "TV_transfrm"))$coeff_value,
         Radio_sales_forecast = Radio_transfrm * (df_model_coeff5 %>% filter(coeff_name == "Radio_transfrm"))$coeff_value,
         Baseline = (df_model_coeff5 %>% filter(coeff_name == "(Intercept)"))$coeff_value) %>% 
   mutate(sales_forecast = rowSums(.[,c("FB_sales_forecast","TV_sales_forecast","Radio_sales_forecast","Baseline")])  )  

df_sales_forecast5
```

#### df Sales contrib

```{r}
df_sales_forecast5 %>% 
  summarise(sales = sum(sales,na.rm = T),
            FB_contrib = sum(FB_sales_forecast, na.rm = T),
            TV_contrib = sum(TV_sales_forecast, na.rm = T),
            Radio_contrib = sum(Radio_sales_forecast, na.rm = T),
            Baseline_contrib = sum(Baseline, na.rm = T),) %>% 
  mutate(total = rowSums(.[,c(2:5)] )) %>% 
  mutate(FB_contrib_perc = FB_contrib/total * 100,
         TV_contrib_perc = TV_contrib/total * 100,
         Radio_contrib_perc = Radio_contrib/total * 100,
         Baseline_contrib_perc = Baseline_contrib/total * 100)
```


#### DW Test for Autocorelatiom

```{r}
car::durbinWatsonTest(model_applied5$finalModel)
```

AS the `p-value > .05` so there is **no autocorrelation** in the model.


#### Residuals Dist. check

```{r}
hist(df_transfrm_applied5$sales-predctn_model_transm5)
```


### 6. Model Log

#### optim log fn call

```{r}
optim(par = c(.1,.1,.1,.1,.1,.1), # initiating a1=.1,a2=.1 & so on till b3=.1
      df_optim = df_optim,
      fn = replicate_excel_solver_log, 
      lower = c(.001,.001,.001,.001,.001,.001),
      upper = c(1,1,1,1,1,1),
      method = "L-BFGS-B")
```


#### alpha beta setting

```{r}
alpha1 = 0.4332286
alpha2 = 0.2605013
alpha3 = 1

beta1 = 1
beta2 = 1
beta3 = 0.0189398
```

```{r}
df_transfrm_applied6 <- df_transfrm %>% 
  mutate(FB_transfrm = FB^alpha1,
         FB_transfrm = if_else(row_number() == 1, 
                               FB^alpha1,
                               ( (FB + lag(FB_transfrm)*beta1)^alpha1 )
                               ) ,
         
         TV_transfrm = TV^alpha2,
         TV_transfrm = if_else(row_number() == 1, 
                               TV^alpha2,
                               ( (TV + lag(TV_transfrm)*beta2)^alpha2 )
                               )  ,
         
         Radio_transfrm = Radio^alpha3,
         Radio_transfrm = if_else(row_number() == 1, 
                               Radio^alpha3,
                               ( (Radio + lag(Radio_transfrm)*beta3)^alpha3 )
                               ) 
         )

df_transfrm_applied6
```

#### model

```{r}
set.seed(2022)

model_applied6 <- caret::train(form = sales ~ log(FB_transfrm)+log(TV_transfrm)+Radio_transfrm,
   data = df_transfrm_applied6, 
   method = "lm") 

model_applied6 %>% 
  summary()
```

```{r}
model_applied6$results
```


As the `Rsq` & MAE values above are not great so not proceeding with this model.

### stargazer results

```{r}
stargazer(model_applied$finalModel,model_applied2$finalModel,
          model_applied4$finalModel,type="text") 
```

```{r}
stargazer(model_applied4$finalModel, model_applied4_2$finalModel,type="text") 
```


```{r}
stargazer(model_applied5$finalModel, model_applied6$finalModel,type="text") 
```

### budget distr

```{r}
Last_budget_fb = df_transfrm_applied[nrow(df_transfrm_applied),"FB"]$FB
Last_budget_tv = df_transfrm_applied[nrow(df_transfrm_applied),"TV"]$TV
Last_budget_radio = df_transfrm_applied[nrow(df_transfrm_applied),"Radio"]$Radio

New_budget_total = 350

New_budget_fb = 100
New_budget_tv = 100
New_budget_radio = New_budget_total - sum(New_budget_fb,New_budget_tv)

a1 = 0.3596438
a2 = 0.8996762
a3 = 0.0010000
b1 = 1.0000000
b2 = 0.0010000
b3 = 0.0010000

transformed_fb = (Last_budget_fb * b1 + New_budget_fb)^a1
transformed_tv = (Last_budget_tv * b2 + New_budget_tv)^a2
transformed_radio = (Last_budget_radio * b3 + New_budget_radio)^a3


contribution_fb = transformed_fb * df_model_coeff[df_model_coeff$coeff_name=="FB_transfrm","coeff_value"]
contribution_tv = transformed_tv * df_model_coeff[df_model_coeff$coeff_name=="TV_transfrm","coeff_value"]
contribution_radio = transformed_radio * df_model_coeff[df_model_coeff$coeff_name=="Radio_transfrm","coeff_value"]
contribution_intercept = df_model_coeff[df_model_coeff$coeff_name=="(Intercept)","coeff_value"]

sales_prediction = sum(contribution_fb,contribution_tv,contribution_radio,contribution_intercept)

CPO = New_budget_total / sales_prediction

CPO
```

### budget distr. fn

```{r}
budget_optimization_fn <- function(params, df_transfrm_applied){
  
  ####### known data cal. starts #######
  New_budget_total = New_budget_fb + New_budget_tv + New_budget_radio
  
  Last_budget_fb = df_transfrm_applied[nrow(df_transfrm_applied),"FB"]$FB
  Last_budget_tv = df_transfrm_applied[nrow(df_transfrm_applied),"TV"]$TV
  Last_budget_radio = df_transfrm_applied[nrow(df_transfrm_applied),"Radio"]$Radio
  
  ####### known data cal. ends #######
  
  
  
  # a is diminishing return & b is adstock for each respective channel
  a1 = 0.3596438
  a2 = 0.8996762
  a3 = 0.0010000
  b1 = 1.0000000
  b2 = 0.0010000
  b3 = 0.0010000
  
  # Unknown params used in below equations
  New_budget_fb = params[1]
  New_budget_tv = params[2]
  New_budget_radio = params[3]
  
  transformed_fb = (Last_budget_fb * b1 + New_budget_fb)^a1
  transformed_tv = (Last_budget_tv * b2 + New_budget_tv)^a2
  transformed_radio = (Last_budget_radio * b3 + New_budget_radio)^a3
  
  
  contribution_fb = transformed_fb * df_model_coeff[df_model_coeff$coeff_name=="FB_transfrm","coeff_value"]
  contribution_tv = transformed_tv * df_model_coeff[df_model_coeff$coeff_name=="TV_transfrm","coeff_value"]
  contribution_radio = transformed_radio * df_model_coeff[df_model_coeff$coeff_name=="Radio_transfrm","coeff_value"]
  contribution_intercept = df_model_coeff[df_model_coeff$coeff_name=="(Intercept)","coeff_value"]
  
  sales_prediction = sum(contribution_fb,contribution_tv,contribution_radio,contribution_intercept)
  
  CPO = (New_budget_fb + New_budget_tv + New_budget_radio) / sales_prediction   # New_budget_total
  
  ## Adding constraint
  
  if(
    New_budget_fb + New_budget_tv + New_budget_radio < 550 & 
    New_budget_fb + New_budget_tv + New_budget_radio > 350
  ){return(CPO)}
  
  return(NA)
  
}
```


```{r}
optim(par = c(100,100,150), # initiating a1=.1,a2=.1 & so on till b3=.1
      df_transfrm_applied = df_transfrm_applied,
      fn = budget_optimization_fn, 
      # lower = c(350,350,350),
      # upper = c(550,550,550),
      method = "L-BFGS-B")
```

```{r}
fn_budget_optim_test <- function(params){
  
  
  # Unknown params used in below equations
  New_budget_fb = params[1]
  New_budget_tv = params[2]
  New_budget_radio = params[3]
  
  New_budget_fb + New_budget_tv + New_budget_radio <= 550  
  New_budget_fb + New_budget_tv + New_budget_radio >= 350
  
  # print(paste("Parameters 1,2,3:",New_budget_fb,New_budget_tv,New_budget_radio))
  
  contribution_fb = ((70.6 * 1.0 + New_budget_fb)^0.3596438) * 2.015733
  contribution_tv = ((16 * 0.001 + New_budget_tv)^0.8996762) * 1.073207
  contribution_radio = (40.8 * 0.001 + New_budget_radio)^0.001 * -6086.523408
  contribution_intercept = 6081.045489
  
  sales_prediction = sum(contribution_fb,contribution_tv,contribution_radio,contribution_intercept)
  
  # print(paste("sales prediction:", sales_prediction))
  
  CPO = (New_budget_fb + New_budget_tv + New_budget_radio) / sales_prediction
  
  # print(paste("CPO:",CPO))
  
  return(CPO)
  
}

optim(par = c(10,10,350),
      fn = fn_budget_optim_test, 
      lower = c(0,0,0),
      # upper = c(550,550,550),
      method = "L-BFGS-B")
```



```{r}
fn_budget_optim_test <- function(params){
  
  
  # Unknown params used in below equations
  New_budget_fb = params[1]
  New_budget_tv = params[2]
  New_budget_radio = params[3]
  
  print(paste("Parameters 1,2,3:",New_budget_fb,New_budget_tv,New_budget_radio))
  
  contribution_fb = ((70.6 * 1.0 + New_budget_fb)^0.3596438) * 2.015733
  contribution_tv = ((16 * 0.001 + New_budget_tv)^0.8996762) * 1.073207
  contribution_radio = (40.8 * 0.001 + New_budget_radio)^0.001 * -6086.523408
  contribution_intercept = 6081.045489
  
  sales_prediction = sum(contribution_fb,contribution_tv,contribution_radio,contribution_intercept)
  
  print(paste("sales prediction:", sales_prediction))
  
  CPO = (New_budget_fb + New_budget_tv + New_budget_radio) / sales_prediction
  
  print(paste("CPO:",CPO))
  
  
  ## Adding constraint
  if(
    (New_budget_fb + New_budget_tv + New_budget_radio) <= 550 & 
    (New_budget_fb + New_budget_tv + New_budget_radio) >= 350
  ) return(CPO)
  
  else return(NA)
}

optim(par = c(10,10,350),
      fn = fn_budget_optim_test, 
      # lower = c(350,350,350),
      # upper = c(550,550,550),
      method = "L-BFGS-B")
```


```{r}
obj_func <- function(params){
  
  # Unknown params used in below equations
  New_budget_fb = params[1]
  New_budget_tv = params[2]
  New_budget_radio = params[3]
  
  print(paste("Parameters 1,2,3:",New_budget_fb,New_budget_tv,New_budget_radio))
  
  contribution_fb = ((70.6 * 1.0 + New_budget_fb)^0.3596438) * 2.015733
  contribution_tv = ((16 * 0.001 + New_budget_tv)^0.8996762) * 1.073207
  contribution_radio = (40.8 * 0.001 + New_budget_radio)^0.001 * -6086.523408
  contribution_intercept = 6081.045489
  
  sales_prediction = sum(contribution_fb,contribution_tv,contribution_radio,contribution_intercept)
  
  print(paste("sales prediction:", sales_prediction))
  
  CPO = (New_budget_fb + New_budget_tv + New_budget_radio) / sales_prediction
  
  print(paste("CPO:",CPO))
  return(CPO)
  
}

  ## Adding constraint

constrain_func <- function(params){
  New_budget_fb = params[1]
  New_budget_tv = params[2]
  New_budget_radio = params[3]
  
  f=NULL
  
  f=rbind(f,New_budget_fb + New_budget_tv + New_budget_radio - 550)  
  f=rbind(f, 350 - (New_budget_fb + New_budget_tv + New_budget_radio))
  return(list(ceq=NULL,c=f))
}

NlcOptim::solnl(c(10,10,350),objfun=obj_func,confun=constrain_func, lb = c(0,0,0))
```

#### Rsolnp:solnp

from: https://stackoverflow.com/questions/30494083/r-optimization-with-equality-and-inequality-constraints

##### Equality

```{r}
opt_func <- function(params){
  
  # Unknown params used in below equations
  New_budget_fb = params[1]
  New_budget_tv = params[2]
  New_budget_radio = params[3]
  
  # print(paste("Parameters 1,2,3:",New_budget_fb,New_budget_tv,New_budget_radio))
  
  contribution_fb = ((70.6 * 1.0 + New_budget_fb)^0.3596438) * 2.015733
  contribution_tv = ((16 * 0.001 + New_budget_tv)^0.8996762) * 1.073207
  contribution_radio = (40.8 * 0.001 + New_budget_radio)^0.001 * -6086.523408
  contribution_intercept = 6081.045489
  
  sales_prediction = sum(contribution_fb,contribution_tv,contribution_radio,contribution_intercept)
  
  # print(paste("sales prediction:", sales_prediction))
  
  CPO = (New_budget_fb + New_budget_tv + New_budget_radio) / sales_prediction
  
  # print(paste("CPO:",CPO))
  return(CPO)
  
}

  ## Adding constraint

equality_func <- function(params){
  New_budget_fb = params[1]
  New_budget_tv = params[2]
  New_budget_radio = params[3]
  
  New_budget_fb + New_budget_tv + New_budget_radio
}

Rsolnp::solnp(c(5,5,5), #starting values (random - obviously need to be positive and sum to 15)
      opt_func, #function to optimise
      eqfun=equality_func, #equality function 
      eqB=350,   #the equality constraint
      LB=c(0,0,0) #lower bound for parameters i.e. greater than zero
      # ,UB=c(100,100,100)) #upper bound for parameters (I just chose 100 randomly)
)
```

##### inEquality

```{r}
opt_func <- function(params){
  
  # Unknown params used in below equations
  New_budget_fb = params[1]
  New_budget_tv = params[2]
  New_budget_radio = params[3]
  
  print(paste("Parameters 1,2,3:",New_budget_fb,New_budget_tv,New_budget_radio))
  
  contribution_fb = ((70.6 * 1.0 + New_budget_fb)^0.3596438) * 2.015733
  contribution_tv = ((16 * 0.001 + New_budget_tv)^0.8996762) * 1.073207
  contribution_radio = (40.8 * 0.001 + New_budget_radio)^0.001 * -6086.523408
  contribution_intercept = 6081.045489
  
  sales_prediction = sum(contribution_fb,contribution_tv,contribution_radio,contribution_intercept)
  
  print(paste("sales prediction:", sales_prediction))
  
  CPO = (New_budget_fb + New_budget_tv + New_budget_radio) / sales_prediction
  
  print(paste("CPO:",CPO))
  return(CPO)
  
}

  ## Adding constraint

equality_func <- function(params){
  New_budget_fb = params[1]
  New_budget_tv = params[2]
  New_budget_radio = params[3]
  
  return(c(New_budget_fb + New_budget_tv + New_budget_radio,
           New_budget_fb + New_budget_tv + New_budget_radio))
            
}

Rsolnp::solnp(c(5,5,5), #starting values (random - obviously need to be positive and sum to 15)
      opt_func, #function to optimise
      eqfun=equality_func, #equality function 
      ineqLB = 350,   #the equality constraint
      ineqUB = 550,
      LB=c(0,0,0) #lower bound for parameters i.e. greater than zero
      # ,UB=c(100,100,100)) #upper bound for parameters (I just chose 100 randomly)
)
```









