---
title: "Market Mix Models - Pharma"
output: 
  html_notebook:
    highlight: tango
    df_print: paged
    toc: true
    toc_float: 
      collapsed: true
      smooth_scroll: true
    number_sections: true
    toc_depth: 6
---



```{r}
library(tidyverse)
library(skimr)
library(caret)
```


```{r}
df1
```

```{r}
df1_mutated <- df1 %>% 
  mutate(compBrand = if_else(compBrand == 4, 1,0)) %>% 
  rename(compBrand_4 = compBrand)
df1_mutated
```



```{r}
df1_monthly_aggr <- df1_mutated %>% 
  select(month, sales:salesVisit5, compBrand_4) %>% 
  group_by(month) %>% 
  summarise_at(vars(sales:compBrand_4), sum, na.rm = TRUE)

df1_monthly_aggr
```

### Adstock & Dim Return

Transform & Optimising function

```{r}
ads_dim_return_solver <- function(params, df){
  
  ads_rate_strategy1 = params[1]
  dim_return_strategy1 = params[2]
  ads_rate_strategy2 = params[3]
  dim_return_strategy2 = params[4]
  ads_rate_strategy3 = params[5]
  dim_return_strategy3 = params[6]
  
  
  ads_rate_salesVisit1 = params[7]
  dim_return_salesVisit1 = params[8]
  ads_rate_salesVisit2 = params[9]
  dim_return_salesVisit2 = params[10]
  ads_rate_salesVisit3 = params[11]
  dim_return_salesVisit3 = params[12]
  ads_rate_salesVisit4 = params[13]
  dim_return_salesVisit4 = params[14]
  ads_rate_salesVisit5 = params[15]
  dim_return_salesVisit5 = params[16]
  
  
  # transforming variables using a,b parameters that need to figured out
  df_optim_tranfm <- df %>% 
  mutate(ads_strategy1 = strategy1^dim_return_strategy1,
         ads_strategy1 = if_else(row_number() == 1, 
                               strategy1^dim_return_strategy1,
                               ( (strategy1 + lag(ads_strategy1)*ads_rate_strategy1)^dim_return_strategy1 )
                               ) ,
         
         ads_strategy2 = strategy2^dim_return_strategy2,
         ads_strategy2 = if_else(row_number() == 1, 
                               strategy2^dim_return_strategy2,
                               ( (strategy2 + lag(ads_strategy2)*ads_rate_strategy2)^dim_return_strategy2 )
                               )  ,
         
         ads_strategy3 = strategy3^dim_return_strategy3,
         ads_strategy3 = if_else(row_number() == 1, 
                               strategy3^dim_return_strategy3,
                               ( (strategy3 + lag(ads_strategy3)*ads_rate_strategy3)^dim_return_strategy3 )
                               )  ,
         ads_salesVisit1 = salesVisit1^dim_return_salesVisit1,
         ads_salesVisit1 = if_else(row_number() == 1, 
                               salesVisit1^dim_return_salesVisit1,
                               ( (salesVisit1 + lag(ads_salesVisit1)*ads_rate_salesVisit1)^dim_return_salesVisit1 )
                               ) ,
         
         ads_salesVisit2 = salesVisit2^dim_return_salesVisit2,
         ads_salesVisit2 = if_else(row_number() == 1, 
                               salesVisit2^dim_return_salesVisit2,
                               ( (salesVisit2 + lag(ads_salesVisit2)*ads_rate_salesVisit2)^dim_return_salesVisit2 )
                               )  ,
         
         ads_salesVisit3 = salesVisit3^dim_return_salesVisit3,
         ads_salesVisit3 = if_else(row_number() == 1, 
                               salesVisit3^dim_return_salesVisit3,
                               ( (salesVisit3 + lag(ads_salesVisit3)*ads_rate_salesVisit3)^dim_return_salesVisit3 )
                               ) ,

		     ads_salesVisit4 = salesVisit4^dim_return_salesVisit4,
         ads_salesVisit4 = if_else(row_number() == 1, 
                               salesVisit4^dim_return_salesVisit4,
                               ( (salesVisit4 + lag(ads_salesVisit4)*ads_rate_salesVisit4)^dim_return_salesVisit4 )
                               ) ,
         
         ads_salesVisit5 = salesVisit5^dim_return_salesVisit5,
         ads_salesVisit5 = if_else(row_number() == 1, 
                               salesVisit5^dim_return_salesVisit5,
                               ( (salesVisit5 + lag(ads_salesVisit5)*ads_rate_salesVisit5)^dim_return_salesVisit5 )
                               ) 
         )
  
         
  # setting seed for lm
  set.seed(2022)
  
  
  # creating model
  model_optim <- lm(sales ~ ads_strategy1+ads_strategy2+ads_strategy3+ads_salesVisit1+ads_salesVisit2+ads_salesVisit3+ads_salesVisit4+ads_salesVisit5, 
                    data = df_optim_tranfm)
  
  # predicted values
  y_hat = predict(model_optim, df_optim_tranfm)

  # MAE that we need to minimize using optim
  MAE <- mean(abs(df_optim_tranfm$sales - y_hat))
  MAE
  
  
}
```


```{r}
optim(par = c(.1,.1,.1,.1,.1,.1,.1,.1,.1,.1,.1,.1,.1,.1,.1,.1), # initiating 
      df = df1_monthly_aggr,
      fn = ads_dim_return_solver, 
      lower = c(.1,.1,.1,.1,.1,.1,.1,.1,.1,.1,.1,.1,.1,.1,.1,.1),
      upper = c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1),
      method = "L-BFGS-B")
```

Using parameters from above to transform vars 

```{r}
  ads_rate_strategy1 = 0.5474243
  dim_return_strategy1 = 0.3269003
  ads_rate_strategy2 = 0.1140976
  dim_return_strategy2 = 0.5154735
  ads_rate_strategy3 = 0.6028481
  dim_return_strategy3 = .1
  
  
  ads_rate_salesVisit1 = 1
  dim_return_salesVisit1 = 1
  ads_rate_salesVisit2 = 1
  dim_return_salesVisit2 = 0.3267252
  ads_rate_salesVisit3 = 0.5443935
  dim_return_salesVisit3 = .1
  ads_rate_salesVisit4 = 0.5145089
  dim_return_salesVisit4 = 0.8343103
  ads_rate_salesVisit5 = 0.5458563
  dim_return_salesVisit5 = 0.5419059
```



```{r}
df1_ads <-  df1_monthly_aggr %>% 
  mutate(ads_strategy1 = strategy1^dim_return_strategy1,
         ads_strategy1 = if_else(row_number() == 1, 
                               strategy1^dim_return_strategy1,
                               ( (strategy1 + lag(ads_strategy1)*ads_rate_strategy1)^dim_return_strategy1 )
                               ) ,
         
         ads_strategy2 = strategy2^dim_return_strategy2,
         ads_strategy2 = if_else(row_number() == 1, 
                               strategy2^dim_return_strategy2,
                               ( (strategy2 + lag(ads_strategy2)*ads_rate_strategy2)^dim_return_strategy2 )
                               )  ,
         
         ads_strategy3 = strategy3^dim_return_strategy3,
         ads_strategy3 = if_else(row_number() == 1, 
                               strategy3^dim_return_strategy3,
                               ( (strategy3 + lag(ads_strategy3)*ads_rate_strategy3)^dim_return_strategy3 )
                               )  ,
         ads_salesVisit1 = salesVisit1^dim_return_salesVisit1,
         ads_salesVisit1 = if_else(row_number() == 1, 
                               salesVisit1^dim_return_salesVisit1,
                               ( (salesVisit1 + lag(ads_salesVisit1)*ads_rate_salesVisit1)^dim_return_salesVisit1 )
                               ) ,
         
         ads_salesVisit2 = salesVisit2^dim_return_salesVisit2,
         ads_salesVisit2 = if_else(row_number() == 1, 
                               salesVisit2^dim_return_salesVisit2,
                               ( (salesVisit2 + lag(ads_salesVisit2)*ads_rate_salesVisit2)^dim_return_salesVisit2 )
                               )  ,
         
         ads_salesVisit3 = salesVisit3^dim_return_salesVisit3,
         ads_salesVisit3 = if_else(row_number() == 1, 
                               salesVisit3^dim_return_salesVisit3,
                               ( (salesVisit3 + lag(ads_salesVisit3)*ads_rate_salesVisit3)^dim_return_salesVisit3 )
                               ) ,

		     ads_salesVisit4 = salesVisit4^dim_return_salesVisit4,
         ads_salesVisit4 = if_else(row_number() == 1, 
                               salesVisit4^dim_return_salesVisit4,
                               ( (salesVisit4 + lag(ads_salesVisit4)*ads_rate_salesVisit4)^dim_return_salesVisit4 )
                               ) ,
         
         ads_salesVisit5 = salesVisit5^dim_return_salesVisit5,
         ads_salesVisit5 = if_else(row_number() == 1, 
                               salesVisit5^dim_return_salesVisit5,
                               ( (salesVisit5 + lag(ads_salesVisit5)*ads_rate_salesVisit5)^dim_return_salesVisit5 )
                               ) 
         )

df1_ads
```

### Model 1

```{r}
df_model <- df1_ads %>% 
  select(sales, contains("ads_"))

df_model
```

#### Model

```{r}
# setting seed for lm
set.seed(2022)

model_1 <- caret::train(sales ~ ., data = df_model, method = "lm")
summary(model_1)
```

#### VIF


```{r}
mctest::imcdiag(model_1$finalModel, method = "VIF")
```


```{r}
# setting seed for lm
set.seed(2022)

model_1_2 <- caret::train(sales ~ ads_strategy1+ads_strategy2+ads_strategy3+ads_salesVisit1+ads_salesVisit3+ads_salesVisit4+ads_salesVisit5, 
                          data = df_model, method = "lm")
summary(model_1_2)
```


```{r}
mctest::imcdiag(model_1_2$finalModel, method = "VIF")
```


#### heteroscadasticity


```{r}
lmtest::bptest(model_1_2$finalModel)
```

No heteroscadasticity in the model as the p-value is greater than 0.05


```{r}
par(mfrow = c(2,2))
plot(model_1_2$finalModel)
```



### Adstock only

```{r}
ads_solver <- function(params, df){
  
  ads_rate_strategy1 = params[1]
   
  ads_rate_strategy2 = params[2]
   
  ads_rate_strategy3 = params[2]
  
  ads_rate_salesVisit1 = params[4]

  ads_rate_salesVisit2 = params[5]

  ads_rate_salesVisit3 = params[6]

  ads_rate_salesVisit4 = params[7]

  ads_rate_salesVisit5 = params[8]

  
  
  # transforming variables using a,b parameters that need to figured out
  df_optim_tranfm <- df %>% 
  mutate(ads_strategy1 = strategy1,
         ads_strategy1 = if_else(row_number() == 1, 
                               strategy1,
                               ( (strategy1 + lag(ads_strategy1)*ads_rate_strategy1) )
                               ) ,
         
         ads_strategy2 = strategy2,
         ads_strategy2 = if_else(row_number() == 1, 
                               strategy2,
                               ( (strategy2 + lag(ads_strategy2)*ads_rate_strategy2) )
                               )  ,
         
         ads_strategy3 = strategy3,
         ads_strategy3 = if_else(row_number() == 1, 
                               strategy3,
                               ( (strategy3 + lag(ads_strategy3)*ads_rate_strategy3) )
                               )  ,
         ads_salesVisit1 = salesVisit1,
         ads_salesVisit1 = if_else(row_number() == 1, 
                               salesVisit1,
                               ( (salesVisit1 + lag(ads_salesVisit1)*ads_rate_salesVisit1) )
                               ) ,
         
         ads_salesVisit2 = salesVisit2,
         ads_salesVisit2 = if_else(row_number() == 1, 
                               salesVisit2,
                               ( (salesVisit2 + lag(ads_salesVisit2)*ads_rate_salesVisit2) )
                               )  ,
         
         ads_salesVisit3 = salesVisit3,
         ads_salesVisit3 = if_else(row_number() == 1, 
                               salesVisit3,
                               ( (salesVisit3 + lag(ads_salesVisit3)*ads_rate_salesVisit3) )
                               ) ,

		     ads_salesVisit4 = salesVisit4,
         ads_salesVisit4 = if_else(row_number() == 1, 
                               salesVisit4,
                               ( (salesVisit4 + lag(ads_salesVisit4)*ads_rate_salesVisit4) )
                               ) ,
         
         ads_salesVisit5 = salesVisit5,
         ads_salesVisit5 = if_else(row_number() == 1, 
                               salesVisit5,
                               ( (salesVisit5 + lag(ads_salesVisit5)*ads_rate_salesVisit5) )
                               ) 
         )
  
         
  # setting seed for lm
  set.seed(2022)
  
  
  # creating model
  model_optim <- lm(sales ~ ads_strategy1+ads_strategy2+ads_strategy3+ads_salesVisit1+ads_salesVisit2+ads_salesVisit3+ads_salesVisit4+ads_salesVisit5, 
                    data = df_optim_tranfm)
  
  # predicted values
  y_hat = predict(model_optim, df_optim_tranfm)

  # MAE that we need to minimize using optim
  MAE <- mean(abs(df_optim_tranfm$sales - y_hat))
  MAE
  
  
}
```


```{r}
optim(par = c(.1,.1,.1,.1,.1,.1,.1,.1), # initiating 
      df = df1_monthly_aggr,
      fn = ads_solver, 
      lower = c(.1,.1,.1,.1,.1,.1,.1,.1),
      upper = c(1,1,1,1,1,1,1,1),
      method = "L-BFGS-B")
```

```{r}

  ads_rate_strategy1 = 0.8629577
   
  ads_rate_strategy2 = 0.9011480
   
  ads_rate_strategy3 = .1
  
  ads_rate_salesVisit1 = 1

  ads_rate_salesVisit2 = 0.6324733

  ads_rate_salesVisit3 = 0.5727674

  ads_rate_salesVisit4 = 0.6053922

  ads_rate_salesVisit5 = 1

  
  
  df1_ads_only <- df1_monthly_aggr %>% 
  mutate(ads_strategy1 = strategy1,
         ads_strategy1 = if_else(row_number() == 1, 
                               strategy1,
                               ( (strategy1 + lag(ads_strategy1)*ads_rate_strategy1) )
                               ) ,
         
         ads_strategy2 = strategy2,
         ads_strategy2 = if_else(row_number() == 1, 
                               strategy2,
                               ( (strategy2 + lag(ads_strategy2)*ads_rate_strategy2) )
                               )  ,
         
         ads_strategy3 = strategy3,
         ads_strategy3 = if_else(row_number() == 1, 
                               strategy3,
                               ( (strategy3 + lag(ads_strategy3)*ads_rate_strategy3) )
                               )  ,
         ads_salesVisit1 = salesVisit1,
         ads_salesVisit1 = if_else(row_number() == 1, 
                               salesVisit1,
                               ( (salesVisit1 + lag(ads_salesVisit1)*ads_rate_salesVisit1) )
                               ) ,
         
         ads_salesVisit2 = salesVisit2,
         ads_salesVisit2 = if_else(row_number() == 1, 
                               salesVisit2,
                               ( (salesVisit2 + lag(ads_salesVisit2)*ads_rate_salesVisit2) )
                               )  ,
         
         ads_salesVisit3 = salesVisit3,
         ads_salesVisit3 = if_else(row_number() == 1, 
                               salesVisit3,
                               ( (salesVisit3 + lag(ads_salesVisit3)*ads_rate_salesVisit3) )
                               ) ,

		     ads_salesVisit4 = salesVisit4,
         ads_salesVisit4 = if_else(row_number() == 1, 
                               salesVisit4,
                               ( (salesVisit4 + lag(ads_salesVisit4)*ads_rate_salesVisit4) )
                               ) ,
         
         ads_salesVisit5 = salesVisit5,
         ads_salesVisit5 = if_else(row_number() == 1, 
                               salesVisit5,
                               ( (salesVisit5 + lag(ads_salesVisit5)*ads_rate_salesVisit5) )
                               ) 
         )
  
  df1_ads_only
```

### Model 2

```{r}
df_model2 <-  df1_ads_only %>% 
  select(sales, contains("ads_"))

df_model2
```


```{r}
# setting seed for lm
set.seed(2022)

model_2 <-  caret::train(sales ~ ., data = df_model2, method = "lm")
summary(model_2)
```

#### VIF

```{r}
mctest::imcdiag(model_2$finalModel, method = "VIF")
```

```{r}
# setting seed for lm
set.seed(2022)

model_2_2 <-  caret::train(sales ~ ads_strategy1+ads_strategy2+ads_strategy3+ads_salesVisit1+ads_salesVisit3+ads_salesVisit4+ads_salesVisit5,
                           data = df_model2, method = "lm")
summary(model_2_2)
```


```{r}
mctest::imcdiag(model_2_2$finalModel, method = "VIF")
```

#### heteroscadasticity


```{r}
lmtest::bptest(model_2_2$finalModel)
```

No heteroscadasticity in the model as the p-value is greater than 0.05


```{r}
par(mfrow = c(2,2))
plot(model_2_2$finalModel)
```



### Model 3 RFE

#### Normalizing Adstock


```{r}
df_train <- df_model2[,]
dim(df_train)
```


Using Range to convert negative values to positive

```{r}
preprocess_step <- caret::preProcess(df_train, method = c("center","scale"))

df_train <- predict(preprocess_step, newdata = df_train)


# To limit range between 0 to 1 & keep it positive
preprocess_step <- caret::preProcess(df_train, method = c("range"))

df_train <- predict(preprocess_step, newdata = df_train)

# to make it normally distributed
preprocess_step <- caret::preProcess(df_train, method = c("BoxCox"))

df_train <- predict(preprocess_step, newdata = df_train)


anyNA(df_train)
```

```{r}
df_train
```


#### RFE


```{r}
set.seed(100)
options(warn=-1)

subsets <- c(1:5, 10, 15)

ctrl <- rfeControl(functions = lmFuncs, #rfFuncs,
                   method = "repeatedcv",
                   repeats = 5,
                   verbose = FALSE)

lmProfile <- rfe(x=df_train %>% select(-sales), y=df_train$sales,
                 sizes = subsets,
                 rfeControl = ctrl)

lmProfile
```

#### Model

```{r}
# setting seed for lm
set.seed(2022)

model_3 <-  caret::train(sales ~ ads_salesVisit1 + ads_salesVisit2 + ads_salesVisit3, 
                         data = df_train, method = "lm")
summary(model_3)
```

#### VIF

```{r}
mctest::imcdiag(model_3$finalModel, method = "VIF")
```

#### heteroscadasticity


```{r}
lmtest::bptest(model_3$finalModel)
```

No heteroscadasticity in the model as the p-value is greater than 0.05


```{r}
par(mfrow = c(2,2))
plot(model_3$finalModel)
```



### Model 4 All vars


#### Normalizing data etc.



```{r}
df_train <- df_model2[,]
dim(df_train)
```


Using Range to convert negative values to positive

```{r}
preprocess_step <- caret::preProcess(df_train, method = c("center","scale"))

df_train <- predict(preprocess_step, newdata = df_train)


# To limit range between 0 to 1 & keep it positive
preprocess_step <- caret::preProcess(df_train, method = c("range"))

df_train <- predict(preprocess_step, newdata = df_train)

# to make it normally distributed
preprocess_step <- caret::preProcess(df_train, method = c("BoxCox"))

df_train <- predict(preprocess_step, newdata = df_train)


anyNA(df_train)
```

```{r}
df_train
```


#### Model

```{r}
# setting seed for lm
set.seed(2022)

model_4 <-  caret::train(sales ~ ., 
                    data = df_train, method = "lm")
summary(model_4)
```

#### vif

```{r}
library(mctest)
```


```{r}
mctest::imcdiag(model_4$finalModel, method = "VIF")
```


```{r}
# setting seed for lm
set.seed(2022)

model_4_2 <-  caret::train(sales ~ ads_strategy1+ads_strategy2+ads_strategy3+ads_salesVisit1+ads_salesVisit3+ads_salesVisit4+ads_salesVisit5, 
                    data = df_train, method = "lm")
summary(model_4_2)
```


```{r}
mctest::imcdiag(model_4_2$finalModel, method= "VIF")
```

#### heteroscadasticity


```{r}
lmtest::bptest(model_4_2$finalModel)
```

No heteroscadasticity in the model as the p-value is greater than 0.05


### Model 5 log

```{r}
df_train <- df_model2[,]
dim(df_train)
```

```{r}
df_train <- log1p(df_train)
df_train
```



Using Range to convert negative values to positive

```{r}
preprocess_step <- caret::preProcess(df_train, method = c("center","scale"))

df_train <- predict(preprocess_step, newdata = df_train)


# To limit range between 0 to 1 & keep it positive
preprocess_step <- caret::preProcess(df_train, method = c("range"))

df_train <- predict(preprocess_step, newdata = df_train)

# to make it normally distributed
preprocess_step <- caret::preProcess(df_train, method = c("BoxCox"))

df_train <- predict(preprocess_step, newdata = df_train)


anyNA(df_train)
```

```{r}
df_train
```


#### Model

```{r}
# setting seed for lm
set.seed(2022)

model_5 <-  caret::train(sales ~ ., 
                    data = df_train, method = "lm")
summary(model_5)
```

#### vif

```{r}
mctest::imcdiag(model_5$finalModel, method = "VIF")
```



```{r}
# setting seed for lm
set.seed(2022)

model_5_2 <-  caret::train(sales ~ ads_strategy2+ads_strategy3+ads_salesVisit1+ads_salesVisit4+ads_salesVisit5, 
                    data = df_train, method = "lm")
summary(model_5_2)
```



```{r}
mctest::imcdiag(model_5_2$finalModel, method = "VIF")
```


#### heteroscadasticity


```{r}
lmtest::bptest(model_5_2$finalModel)
```

No heteroscadasticity in the model as the p-value is greater than 0.05


### Model 6 log RFE


```{r}
df_train <- df_model2[,]
dim(df_train)
```

```{r}
df_train <- log1p(df_train)
df_train
```


#### Normalizing Adstock

Using Range to convert negative values to positive

```{r}
preprocess_step <- caret::preProcess(df_train, method = c("center","scale"))

df_train <- predict(preprocess_step, newdata = df_train)


# To limit range between 0 to 1 & keep it positive
preprocess_step <- caret::preProcess(df_train, method = c("range"))

df_train <- predict(preprocess_step, newdata = df_train)

# to make it normally distributed
preprocess_step <- caret::preProcess(df_train, method = c("BoxCox"))

df_train <- predict(preprocess_step, newdata = df_train)


anyNA(df_train)
```

```{r}
df_train
```


#### RFE


```{r}
set.seed(100)
options(warn=-1)

subsets <- c(1:5, 10, 15)

ctrl <- rfeControl(functions = lmFuncs, #rfFuncs,
                   method = "repeatedcv",
                   repeats = 5,
                   verbose = FALSE)

lmProfile <- rfe(x=df_train %>% select(-sales), y=df_train$sales,
                 sizes = subsets,
                 rfeControl = ctrl)

lmProfile
```


#### Model

```{r}
# setting seed for lm
set.seed(2022)

model_6 <-  caret::train(sales ~ ads_strategy1+ads_strategy2+ads_salesVisit1+ads_salesVisit2+ads_salesVisit3, 
                    data = df_train, method = "lm")
summary(model_6)
```

#### vif

```{r}
mctest::imcdiag(model_6$finalModel, method = "VIF")
```



```{r}
# setting seed for lm
set.seed(2022)

model_6_2 <-  caret::train(sales ~ ads_strategy2+ads_salesVisit1+ads_salesVisit2+ads_salesVisit3, 
                    data = df_train, method = "lm")
summary(model_6_2)
```



```{r}
mctest::imcdiag(model_6_2$finalModel, method = "VIF")
```


```{r}
# setting seed for lm
set.seed(2022)

model_6_3 <-  caret::train(sales ~ ads_strategy2+ads_salesVisit1+ads_salesVisit3, 
                    data = df_train, method = "lm")
summary(model_6_3)
```


```{r}
mctest::imcdiag(model_6_3$finalModel, method = "VIF")
```


### Model 7 All data

```{r}
df1_ads_only
```

#### Normalizing Adstock

As qty is highly correlated to sales & qty is also unknown when predicting sales so not selecting qty in training dataset.

```{r}
df_train <- df1_ads_only %>% 
  select(-c(month, qty))

df_train
```


```{r}
dim(df_train)
```


Using Range to convert negative values to positive

```{r}
preprocess_step <- caret::preProcess(df_train, method = c("center","scale"))

df_train <- predict(preprocess_step, newdata = df_train)


# To limit range between 0 to 1 & keep it positive
preprocess_step <- caret::preProcess(df_train, method = c("range"))

df_train <- predict(preprocess_step, newdata = df_train)

# to make it normally distributed
preprocess_step <- caret::preProcess(df_train, method = c("BoxCox"))

df_train <- predict(preprocess_step, newdata = df_train)


anyNA(df_train)
```

```{r}
df_train
```


#### RFE


```{r}
set.seed(100)
options(warn=-1)

subsets <- c(1:5, 10, 15)

ctrl <- rfeControl(functions = lmFuncs, #rfFuncs,
                   method = "repeatedcv",
                   repeats = 5,
                   verbose = FALSE)

lmProfile <- rfe(x=df_train %>% select(-sales), y=df_train$sales,
                 sizes = subsets,
                 rfeControl = ctrl)

lmProfile
```


#### Model

```{r}
# setting seed for lm
set.seed(2022)

model_7 <-  caret::train(sales ~ strategy3+ads_strategy3+ads_salesVisit2+ads_salesVisit3, 
                         data = df_train, method = "lm")
summary(model_7)
```


#### VIF

```{r}
mctest::imcdiag(model_7$finalModel, method = "VIF")
```



```{r}
# setting seed for lm
set.seed(2022)

model_7_2 <-  caret::train(sales ~ ads_strategy3+ads_salesVisit2+ads_salesVisit3, 
                         data = df_train, method = "lm")
summary(model_7_2)
```

```{r}
mctest::imcdiag(model_7_2$finalModel,method = "VIF")
```


#### heteroscadasticity


```{r}
lmtest::bptest(model_7_2$finalModel)
```

No heteroscadasticity in the model as the p-value is greater than 0.05

### Timeseries

```{r}
library(forecast)
```


```{r}
df1_ads_only
```

```{r}
ts_sales <- ts(df1_ads_only$sales, start = c(2013, 10), frequency = 12)
ts_sales
```


```{r}
ts_sales_comp <- decompose(ts_sales)
```

```{r}
ts_sales_comp
```

```{r}
ts_sales_comp$trend
```

```{r}
data.frame(Trend=as.matrix(ts_sales_comp$trend), date= zoo::as.Date(time(ts_sales_comp$trend)))
```

```{r}
data.frame(Seasonal=as.matrix(ts_sales_comp$seasonal), date= zoo::as.Date(time(ts_sales_comp$trend)))
```

```{r}
plot(ts_sales_comp)
```

### Model 8


```{r}
model_8 <- tslm(ts_sales ~ trend + season) 

summary(model_8)
```

### Model 9


```{r}
model_9 <- tslm(ts_sales ~ trend + season + ads_strategy1 + ads_strategy2 + ads_strategy3, data = df_train) 
 
summary(model_9)
```


```{r}
model_9 <- tslm(ts_sales ~ trend + season + ads_strategy1+ads_strategy2+ads_strategy3+salesVisit1+salesVisit2+salesVisit3+salesVisit4+salesVisit5,
                data = df_train) 
 
summary(model_9)
```


```{r}
mctest::imcdiag(model_9, method = "VIF")
```


```{r}
car::vif(model_9)
```


```{r}
tslm(ts_sales ~ trend, data = df_train) %>% 
  summary()
```

```{r}
tslm(ts_sales~., data = df_train) %>% 
  summary()
```

### Model 10

```{r}
library(forecast)
```


```{r}
df1_ads_only
```



Using Range to convert negative values to positive

```{r}
preprocess_step <- caret::preProcess(df1_ads_only, method = c("center","scale"))

df_train <- predict(preprocess_step, newdata = df1_ads_only)


# To limit range between 0 to 1 & keep it positive
preprocess_step <- caret::preProcess(df_train, method = c("range"))

df_train <- predict(preprocess_step, newdata = df_train)

# to make it normally distributed
preprocess_step <- caret::preProcess(df_train, method = c("BoxCox"))

df_train <- predict(preprocess_step, newdata = df_train)


anyNA(df_train)
```



```{r}
ts_sales <- ts(df_train$sales, start = c(2013, 10), frequency = 12)
ts_sales
```


```{r}
ts_sales_comp <- decompose(ts_sales)
```

```{r}
ts_sales_comp
```


```{r}
plot(ts_sales_comp)
```

```{r}
ts_sales_comp$trend
```

```{r}
Trend_comp <- data.frame(Trend=as.matrix(ts_sales_comp$trend), date= zoo::as.Date(time(ts_sales_comp$trend))) %>% 
  pull(Trend)

Trend_comp
```

```{r}
Seasonal_comp <- data.frame(Seasonal=as.matrix(ts_sales_comp$seasonal), 
           date= zoo::as.Date(time(ts_sales_comp$trend))) %>% 
  pull(Seasonal)

Seasonal_comp
```


#### Model


```{r}
model_10 <- tslm(ts_sales ~ Trend_comp + Seasonal_comp + ads_strategy1 + ads_strategy2 + ads_strategy3,
                 data = df_train) 

summary(model_10)
```


```{r}
model_10_2 <- tslm(ts_sales ~ Trend_comp + Seasonal_comp,
                 data = df_train) 

summary(model_10_2)
```

